\documentclass{article}

\title{Personalities to NPC behaviour}
\date{8-09-2016}
\author{Steven Schenk}

\usepackage{fancyhdr}
\usepackage{parskip}



\pagestyle{fancy}
\fancyhead[L]{Personality behaviour}


\begin{document}
\pagenumbering{gobble}
\maketitle
\newpage
\pagenumbering{arabic}
\tableofcontents

\newpage
\section{Introversion}

Introverds, are not by definition unsociable, but they won't bend your ear. This does not
necessarily mean they are shy. They behave very calm, and want to be rather alone then
then in big company. \cite{bigfive} Introverds are much more sensitive to the enviroment. \cite{introverie}

\subsection{Characteristics}
\begin{enumerate}
\item Rather alone, walks away from people 
\item Calm 
\item Does not like to be in the spotlight
\end{enumerate} 

\subsection{NPC behaviour}
\begin{enumerate}
\item Avoiding company, walks away from other characters/npc
\item Doesn't move that much, stays on his position 
\item Move to the corners of a space, not to the center
\item Doesn't start a conversation
\item When in a conversation, he doesn't say much
\end{enumerate} 

\section{Extraversion}

An extroverted person is very social towards others and likes hanging out and having chit chats.
They are cheerful all the time and have a very optimistic way of looking at things. \cite{extraversie}

\subsection{Characteristics}
\begin{enumerate}
\item Friendly 
\item Seeking for company
\item Happy
\item Alive 
\item Leading person / Speaks a lot
\end{enumerate} 

\subsection{NPC behaviour}
\begin{enumerate}
\item Move towards other characters/npc 
\item Moves a lot, very alive
\item Stay in the center of spaces
\item Starts a conversation
\item Speaks a lot
\end{enumerate} 

\section{Altruism}
Altruism is the ability to have compassion with other people. Altruistic people show
respect towards other people. They are honest and are always willing to lend a hand and care
for people needing help. \cite{altruisme} 

\subsection{Characteristics}
\begin{enumerate}
\item Considerate 
\item Honest
\item Respect to the peoples 
\end{enumerate} 

\subsection{NPC behaviour}
\begin{enumerate}
\item Walk towards NPC/characters needing help
\item Tell the truth
\item Step aside for other people
\end{enumerate} 

\section{Egoism}
In philosophy, egoism is the theory that one’s self is, or should be, the motivation and the goal of one’s own action. \cite{egoism}
Egoistic people do not really care about other people. They can behave agressive, arrogant and might even tell you a lie 
to make them look better. \cite{bigfive}

\subsection{Characteristics}
\begin{enumerate}
\item Don't care about other peoples problems
\item Not completely honest 
\item Agressive 
\item Arrogant 
\item No compassion
\end{enumerate} 

\subsection{NPC behaviour}
\begin{enumerate}
\item Walking away of people needing help
\item Tell lies
\item Don't take other people into account when moving 
\end{enumerate}

\section{Thoroughness}
People that are organized and very targeted. They are both ambitious and trustworthy.
They see life as task to fulfill and are determinded to complete in these tasks. \cite{bigfive}

\subsection{Characteristics}
\begin{enumerate}
\item Precise
\item Trustworthy 
\item perseverance 
\item Careful
\end{enumerate} 

\subsection{NPC behaviour}
\begin{enumerate}
\item Does not tell (many) lies
\end{enumerate} 



\section{Chaotic}

Chaotic people are very disorganized and are willing to bend the rules. They do not 
experience stress, even if they are failing in their tasks. They are very flexible. \cite{bigfive}

\subsection{Characteristics}
\begin{enumerate}
\item Disorganized
\item Quitters
\item Flexible 
\end{enumerate} 

\subsection{NPC behaviour}
\begin{enumerate}
\item ??
\end{enumerate} 

\section{Neuroticism}
Neuroticism is a long-term tendency to be in a negative emotional state. Neurotics
tend to have more depressed moods. They suffer from feelings as guilt, envy, anger and anxiety. 
They are very sensitive sensitive to enviromental sensitive. \cite{neuroticism}

\subsection{Characteristics}
\begin{enumerate}
\item Depressed moods
\item Shy, self-conscious
\item Emotional instable
\end{enumerate} 

\subsection{NPC behaviour}
\begin{enumerate}
\item Hide in the corners of a space
\item Cries out of nothing
\item Cries in stressful situations
\end{enumerate} 

\section{Emotional stable}

Emotional stable people do not worry fast and are very stable in what they doing. You can not get
them out of their flow easily. They are pleased with themselfs and tend to be very calm in stresful
situations. \cite{bigfive}

\subsection{Characteristics}
\begin{enumerate}
\item Calm
\item Relaxed
\item Pleased with themself
\end{enumerate} 

\subsection{NPC behaviour}
\begin{enumerate}
\item Remain calm in stresful situations
\end{enumerate} 

\newpage
\bibliography{personalities}
\bibliographystyle{siam}

\end{document}